A non-contextual hidden variable model for QM

### 2016-07-06 finalPaper.tex
added the block diagram and included the quick description of the work

\AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
\AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
\RS@ifundefined{subref}
  {\def\RSsubtxt{section~}\newref{sub}{name = \RSsubtxt}}
  {}
\RS@ifundefined{thmref}
  {\def\RSthmtxt{theorem~}\newref{thm}{name = \RSthmtxt}}
  {}
\RS@ifundefined{lemref}
  {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
  {}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{xcolor}
%\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

@@

Triangle: <TODO: ask arvind sir>

Work and results: <summarise what is done in each section>

\section{Context}

@@

\section{Non-Multiplicativity: An alternative to Contextuality}

@@

\subsection{C-ingle model | An Explicit Construction}

@@

\subsection{Non-contextual Bohmain Mechanics}

@@

\section{Implications}

>>>>

\AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
\AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
\AtBeginDocument{\providecommand\figref[1]{\ref{fig:#1}}}
\AtBeginDocument{\providecommand\secref[1]{\ref{sec:#1}}}
\AtBeginDocument{\providecommand\ssecref[1]{\ref{ssec:#1}}}

\RS@ifundefined{subref}
  {\def\RSsubtxt{section~}\newref{sub}{name = \RSsubtxt}}
  {}
\RS@ifundefined{thmref}
  {\def\RSthmtxt{theorem~}\newref{thm}{name = \RSthmtxt}}
  {}
\RS@ifundefined{lemref}
  {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
  {}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{graphicx}
\graphicspath{ {images/} }

\usepackage{xcolor}
%\usepackage{url}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

@@

Triangle: <TODO: ask arvind sir, see \figref{block}>

\begin{figure}[h]
\includegraphics[width=\columnwidth]{block1}
\caption{Non-contextuality is not inconsistent with QM}
\label{fig:block}\end{figure}

Work and results: In \secref{context} we establish a notation and definitions to facilitate further discussions. In \secref{nonMultiplicativity} we introduce the notion of multiplicativity and that of sequential multiplicativity. We review the `contextuality' theorem and prove some results about multiplicativity. We construct an explicit non-contextual model in \ssecref{cingle} and apply it to the very proof of `contextuality' to illustrate non-multiplicativity. This is supplemented by a discussion about Bohmian Mechanics in \ssecref{nonContBohm} where contextuality is removed by hand. The paper is concluded with discussion of implications of multiplicativity on locality, entanglement, superposition and apparent contextuality in \secref{implications}.

\section{Context \label{sec:context}}

@@

\section{Non-Multiplicativity: An alternative to Contextuality \label{sec:nonMultiplicativity}}

@@

\subsection{C-ingle model | An Explicit Construction \label{ssec:cingle}}

@@

\subsection{Non-contextual Bohmain Mechanics \label{ssec:nonContBohm}}

@@

\section{Implications \label{sec:implications}}
